%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Template: Curriculum Vitae
%
% Source: http://www.howtotex.com/
% Feel free to distribute this template, but please keep the
% referal to HowToTeX.com.
% Date: July 2011
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX: 
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% If you're new to LaTeX, the wikibook is a great place to start:
% http://en.wikibooks.org/wiki/LaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[paper=a4,fontsize=9pt]{scrartcl} % KOMA-article class
							
	\usepackage[english]{babel}
	\usepackage[utf8x]{inputenc}
	\usepackage[protrusion=false,expansion=true]{microtype}
	\usepackage{amsmath,amsfonts,amsthm}     % Math packages
	\usepackage{graphicx}                    % Enable pdflatex
	\usepackage[svgnames]{xcolor}            % Colors by their 'svgnames'
	\usepackage{geometry}
		\textheight=1400px                    % Saving trees ;-)
	\usepackage{url}
	\geometry{
		top=10mm,
	}
	
	\frenchspacing              % Better looking spacings after periods
	\pagestyle{empty}           % No pagenumbers/headers/footers
	
	%%% Custom sectioning (sectsty package)
	%%% ------------------------------------------------------------
	\usepackage{sectsty}
	
	\sectionfont{%			            % Change font of \section command
		\usefont{OT1}{phv}{b}{n}%		% bch-b-n: CharterBT-Bold font
		\sectionrule{0pt}{0pt}{-5pt}{3pt}}
	
	%%% Macros
	%%% ------------------------------------------------------------
	\newlength{\spacebox}
	\settowidth{\spacebox}{8888888888}			% Box to align text
	\newcommand{\sepspace}{\vspace*{0.8em}}		% Vertical space macro
	
	\newcommand{\MyName}[1]{ % Name
			\Huge \usefont{OT1}{phv}{b}{n} \hfill #1
			\par \normalsize \normalfont}
			
	\newcommand{\MySlogan}[1]{ % Slogan (optional)
			\large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1}
			\par \normalsize \normalfont}
	
	\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

	\newcommand{\PersonalEntry}[2]{
			\noindent\hangindent=2em\hangafter=0 % Indentation
			\parbox{\spacebox}{        % Box to align text
			\textit{#1}}		       % Entry name (birth, address, etc.)
			\hspace{1.5em} #2 \par}    % Entry value

	\newcommand{\PersonalStatement}[2]{
			\noindent\hangindent=0em\hangafter=0 % Indentation
			\parbox{\spacebox}{        % Box to align text
			\textit{#1}}		       % Entry name (birth, address, etc.)
			\hspace{-5.5em} #2 \par}    % Entry value

	\newcommand{\SkillsEntry}[2]{      % Same as \PersonalEntry
			\noindent\hangindent=2em\hangafter=0 % Indentation
			\parbox{\spacebox}{        % Box to align text
			\textit{#1}}			   % Entry name (birth, address, etc.)
			\hspace{1.5em} #2 \par}    % Entry value	

	\newcommand{\EducationEntry}[4]{
			\noindent {#1} \hfill      % Study
			\colorbox{Black}{%
				\parbox{6em}{%
				\hfill\color{White}#2}} \par  % Duration
			\noindent \textit{#3} \par        % School
			\noindent\hangindent=2em\hangafter=0 \small #4 % Description
			\normalsize \par}

	\newcommand{\WorkEntry}[4]{				  % Same as \EducationEntry
			\noindent {#1} \hfill      % Jobname
			\colorbox{White}{\color{Black}#2} \par  % Duration
			\noindent \textit{#3} \par              % Company
			\noindent\hangindent=2em\hangafter=0 \small #4 % Description
			\normalsize \par}
	
	%%% Begin Document
	%%% ------------------------------------------------------------
	\begin{document}

	\MyName{Brian Fitzgerald}

	\sepspace

	%%% Personal details
	%%% ------------------------------------------------------------
	\NewPart{Personal details}{}

	\PersonalEntry{Location}{Columbia, MO / Remote}
	\PersonalEntry{Phone}{(618) 616-3533}
	\PersonalEntry{Mail}{\url{brianfitzgerald242@gmail.com}}
	\PersonalEntry{GitHub}{\url{https://github.com/brianfitzgerald}}

	%%% Work experience
	%%% ------------------------------------------------------------
	\NewPart{Work experience}{}

	\WorkEntry{Machine Learning Engineer}{2022 - }{Stability AI}{
		\begin{itemize}
			\item Worked on the fine-tuning API for Stability's Stable Diffusion range of generative image models. Developed an inference, fine-tuning and post-processing stack that led to best-in-class fine-tuning training times, and best-in-industry image fidelity. This API is being trialed with several large enterprise customers.
			\item Wrote and trained a series of content classifiers to filter out NSFW generations from Stability's image generation APIs. Achieved state-of-the-art inference times with minimal hit to model performance. Developed a system to detect model drift and retrain the model based on user activity patterns.
			\item Designed and single-handedly wrote Stability for Blender, and maintained Stability for Photoshop, both efforts to integrate Stability's generative image models into professional workflows.
			\item Worked on Stability's next-generation inference platform, as well as model compilation strategies to bring inference times and memory usage in line with industry standards.
		\end{itemize}
	}
	\sepspace

	\WorkEntry{Senior Software Engineer, Robotics}{2020 - 2022}{EquipmentShare}{
		\begin{itemize}
			\item Worked on various computer vision tasks for an autonomous construction system, including filtering and segmentation of LIDAR and image data in C++ and Python.
			\item Developed and maintained a distributed simulation environment for testing and developing autonomous construction equipment, including a highly performant LIDAR simulator and test scenario generator with Mujoco and Unity.
			\item Wrote and implemented a system for training large scale Computer Vision models based on validation and testing data gathered from real-world testing.
			\item Developed a pipeline for the recording and replay of sensor data from physical machines, including a real-time visualization system for reviewing defects and anomalies in training data.
			\item Designed and implemented a custom video streaming solution intended for low-bandwidth use, streaming video from the robot's cameras to a remote client, as well as other services on the machine.
			\item Mentored a team of interns in developing a custom depth estimation and segmentation system for obstacle detection from video data.
		\end{itemize}
	}
	\sepspace

	\WorkEntry{Senior Software Engineer, Elogs}{2019 - 2020}{EquipmentShare}{
		\begin{itemize}
			\item Worked on expanding support for the Elogs ELD compliance system, which gave real-time alerts for FMCSA guideline violations to thousands of drivers. Grew the list of supported state regulations from 2 to 30.
			\item Maintained the React Native - based iOS and Android Elogs app, which served a wide range of mobile devices and trackers.
			\item Coordinated with other teams within the company to expand DOT regulation support across multiple products.
			\item Maintained a front-end and API for fleet managers to manage their drivers in React and TypeScript.
		\end{itemize}
	}
	\sepspace

	\WorkEntry{Software Engineer}{2016 - 2019}{CARFAX}{
		\begin{itemize}
			\item Led the development of the CARFAX Service Shops application, which provides shops with a toolset for managing customer-facing data for their shop and viewing analytics.
			\item Designed and implemented a package-based frontend architecture for myCARFAX's core products over the span of several project timelines. Developed a standard for sharing common functionality across products and teams.
			\item Created an architecture for one of CARFAX's first user-facing products running on Amazon Web Services. Collaborated on the strategy for migrating the CARFAX's on-premises consumer services to an AWS-managed, Kubernetes-based infrastructure.
			\item Worked on the rewrite of myCARFAX's core web applications from Angular to React/Redux. Worked with the User Experience team to enforce a consistent look and feel across myCARFAX products.
			\item Led the development of the CARFAX Service Shops application, written in React / Node / Typescript, which is used by 1,000s of customers daily.
		\end{itemize}
	}
	\sepspace

	\WorkEntry{Developer}{February 2018 - January 2019}{InteraXon Inc}{
		\begin{itemize}
			\item Developed the CES demo experience for the MUSE 2 by Interaxon, an AR experience that allows users to try out a virtual version of the headset and explore its features. Built in {Unity} with {ARKit}, utilizing face detection and masking.
			\item Was later deployed in demo kiosks in California, and integrated into InteraXon's marketing material.
		\end{itemize}
	}
	\sepspace

	\WorkEntry{Developer}{September 2018 - February 2019}{Healium XR}{
		\begin{itemize}
			\item Designed and developed several AR experiences for assisting with meditation in Unity with ARKit and ARCore, targeting mobile devices and the Oculus Go headset.
			\item Built a dashboard and analytics platform for tracking biometric data. Used AWS Cognito for authentication and Lambda and DynamoDB for the backend.
		\end{itemize}
	}
	\sepspace

	\WorkEntry{Developer}{June 2017 - May 2018}{GeneTrait Laboratories}{
		\begin{itemize}
			\item Developed the MedTrait reporting system for GeneTrait.
			\item Developed a backend service to generate genetic testing reports with Node / Express, as well as a component library in React and Typescript to render the reports.
			\item Was involved in the entire product development cycle, including designing features and developing a user experience and visual identity.
		\end{itemize}
	}
	\sepspace

	\WorkEntry{Developer}{Oct 2015 - Jun 2016}{QuarkWorks}{
		\begin{itemize}
			\item Worked on a variety of native mobile applications, including ZephyrCharts, an aviation mapping application for pilots. This involved developing native iOS and Android clients for each project.
			\item Developed the companion app for Columbia's local Roots n Blues festival, as well as a backend for managing user data in Google Cloud.
		\end{itemize}
	}
	\sepspace
	
	\WorkEntry{Software Developer}{Feb 2014 - Sep 2015}{WireCloud, LLC}{
		\begin{itemize}
			\item Worked on various contracting projects including the backend for a local food delivery service. Built a system for managing a stream of orders, and assigning them to drivers, as well as a customer-facing order tracking system. 
			\item Developed a companion mobile web application for drivers.
		\end{itemize}
	}
	\sepspace
	
	%%% Skills
	%%% ------------------------------------------------------------
	\NewPart{Skills and Technologies}{}
	
	\SkillsEntry{Frontend}{TypeScript, React, Redux, MobX, Webpack}
	
	\SkillsEntry{Vision}{PCL, Tensorflow, Pytorch, OpenCV, OpenGL, Unity}
	\SkillsEntry{Robotics}{C++, Rust, ZeroMQ, Protobuf, ROS, Waymo Honeycomb}
	\SkillsEntry{Backend}{Express, Golang, Terraform, Kubernetes, Helm, Jenkins, Docker}
	\SkillsEntry{AWS}{SQS, CloudFront / S3, ECS, Lambda, Cognito}

	\SkillsEntry{Mobile}{Swift / iOS, Android SDK, SceneKit}

	\SkillsEntry{XR}{Unity, C\#, ShaderLab, ARKit / ARCore, SteamVR SDK}

	\NewPart{Education}{}
	
	\WorkEntry{Governor French Academy}{2011 - 2015}{High School}{
	}
	\WorkEntry{University of Missouri}{2016 - 2017}{College, Not Completed}{
	}
	\sepspace
	\end{document}
	
	
	